A new breeding crossover approach for evolutionary algorithms

### 2023-09-22 paper.tex
Afternoon Updates.

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
        \caption{Animal Life Cycle Algorithm model\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
        \end{figure}

@@

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Animal Life Cycle Algorithm (ALCA) General Configuration.}\label{tab.general_configuration}    
    \begin{tabular}{@{}ll@{}}
    \toprule
    \multicolumn{2}{l}{\textbf{ALCA   General Configuration}} \\ \midrule
    \textbf{Function name} & \textbf{ALL} \\
    Population & 500 \\
    Evaluations & 10,000 * Dim \\
    Crossover rate & 100 \\
    Mutation rate & 7 \\
    Max age & 5 \\
    Tournament rep. & 100 \\
    Sample size & 20 \\
    Base approval & 80 \\
    Goal approval & 200 \\ \bottomrule
    \end{tabular}
    \end{table}

>>>>

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_algorithm_model.pdf}
        \caption{General model concept for the Animal Life Cycle Algorithm (ALCA)\cite{Felix-Saul2023}.} \label{fig.algorithm_model}
        \end{figure}

@@

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Animal Life Cycle Algorithm (ALCA) General Configuration.}\label{tab.general_configuration}    
    \begin{tabular}{@{}ll@{}}
    \toprule
    \multicolumn{2}{l}{\textbf{ALCA   General Configuration}} \\ \midrule
    \textbf{Dimensions Evaluated} & \textbf{10, 30} \\
    Population' Individuals & 500 \\
    Maximum Evaluations & 10,000 * Dim \\
    Rate for Crossover & 100 \\
    Rate for Mutation & 7 \\
    Maximum Age & 5 \\
    Rate for Tournament & 100 \\
    Size of Sample & 20 \\
    Minimum Approval & 80 \\
    Maximum Approval & 200 \\ \bottomrule
    \end{tabular}
    \end{table}
